My title

### 2024-12-01 paper/paper.qmd
Updated PDF of paper with new changes to model section

We use the statistical programming language R [@citeR].... Our data [@datahomicides].... Following @citetellingstories, we consider...

@@

## Model set-up
With our model, we will make the assumption that there is a relationship between homicide case information like the victim's race, victim's age, victim's sex, the city, and the year with a homicide case being unsolved. We also assume that the predictor variables are independent from one another, which we check in [Appendix -@sec-model-details] using variance inflation factor (VIF) and it indicates the predictors are not highly correlated with each other. We define our model as follows:

\begin{align*} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \beta_0 + \beta_1 \times \mbox{victim_race}_i + \beta_2 \times \mbox{victim_age}_i + \beta_3 \times \mbox{victim_sex}_i + \beta_4 \times \mbox{city}_i + \beta_5 \times \mbox{year}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \\
\end{align*}

We define $y_i$ to be the status of the homicide case where 1 means the homicide is unsolved (case is still open / been closed without arrest) and 0 means the homicide is solved (case has been closed with arrest). $\pi_i$ represents the probability of the homicide being solved. $\mbox{logit}(\pi_i)$ indicates the log-odds of the homicide being unsolved. Now looking at the coefficients $b_i$ and predictor variables, $\beta_0$ is the intercept of our model and is the log-odds when all predictor variables are equal to 0. $\mbox{victim_race}_i$ signifies the race of the victim, which could be either "Asian", "Black", "Hispanic", "White", and "Other". In our model, we use "White" as the baseline for $\mbox{victim_race}_i$ to see if being part of a minority impacts if the case goes unsolved or not. $beta_1$ is the coefficient that represents the log-odds when $\mbox{victim_race}_i$ changes. $\mbox{victim_age}_i$ is the victim's age, which is a whole number. $beta_2$ is the log-odds when $\mbox{victim_age}_i$ increases by 1 year. $\mbox{victim_sex}_i$ represents the sex of the victim, where in the dataset it is either "female" or "male" and $\beta_3$ is the log-odds when $\mbox{victim_sex}_i$ changes. $\mbox{city}_i$ is the city the victim was reported to be killed in, which from our dataset could be either "New York" or "Los Angeles". $beta_4$ is the coefficient that stands for the log-odds when $\mbox{city}_i$ changes. We define $\mbox{year}_i$ to be the year the homicide was reported to have occured from 2010 to 2017. $\beta_5$ indicates the log-odds when $\mbox{year}_i$ increases by 1 year.

Our model runs in R [@citeR] using the rstanarm package [@citerstanarm]. For our model's priors, we use the default priors provided by rstanarm [@citerstanarm]. Diagnostics for the model such as in posterior predictive check, posterior versus prior comparison, trace and Rhat plots can be found in [Appendix -@sec-model-details].

@@

# NOTE: Needed to save diagram and read it in as an image since grViz doesn't render in PDFs
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("../other/sketches/casual_model.png")
plot.new()
rasterImage(the_image, 0,0,1.05,1)
```
However, our model has limitations and there are situations where this model would not work. In @fig-causal-model, it shows that there is a confounder, "resources of investigating team" between the predictor variables, city and year and the outcome variable, case being unsolved. We define "resources of the investigating team" to include any of the following: the amount of people on the team investigating the case, time available allotted to investigate the case, amount of open cases for the team, cost, skill and education levels of members, etc. We currently do not have any information available about the resources of the investigating team for the case and further investigation is needed. We proposed an idealized survey we would conduct to collect the necessary data to further understand the relationship between homicide case characteristics and unsolved homicides in @subsec-ideal-survey. If we have information available about the resources of the investigating team for the case, the current model would not work and would need to be revised. This is due to the interaction between the city, year, and outcome variables with the confounder.

@@

\newpage
## Idealized Survey and Methodology {#subsec-ideal-survey}
- Link to literature

@@

\newpage 
## Overview and Evaluation of The Washington Post’s Dataset {@subsec-data-evalulation}
- TODO: Make sure to link evaluation to literature

>>>>

The data we used for this paper comes from The Washington's Post's GitHub repository, "How The Post mapped unsolved murders" also known as the "Unsolved Homicide Database" [@datahomicides]. For the entirety of the paper, we used the statistical programming language R [@citeR]. We also used

@@

## Model set-up
With our model, we will make the assumption that there is a relationship between homicide case information like the victim's race, victim's age, victim's sex, the city, and the year with a homicide case being unsolved. We also assume that the predictor variables are independent from one another, which we check in @sec-model-details using variance inflation factor (VIF) and it indicates the predictors are not highly correlated with each other. We define our model as follows:

\begin{align*}
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \beta_0 + \beta_1 \times \mbox{victim\_race}_i + \beta_2 \times \mbox{victim\_age}_i + \beta_3 \times \mbox{victim\_sex}_i + \beta_4 \times \mbox{city}_i + \beta_5 \times \mbox{year}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
\beta_5 &\sim \mbox{Normal}(0, 2.5)
\end{align*}

We define $y_i$ to be the status of the homicide case where 1 means the homicide is unsolved (case is still open / been closed without arrest) and 0 means the homicide is solved (case has been closed with arrest). $\pi_i$ represents the probability of the homicide being solved. $\mbox{logit}(\pi_i)$ indicates the log-odds of the homicide being unsolved. Now looking at the coefficients $b_i$ and predictor variables, $\beta_0$ is the intercept of our model and is the log-odds when all predictor variables are equal to 0. $\mbox{victim\_race}_i$ signifies the race of the victim, which could be either "Asian", "Black", "Hispanic", "White", and "Other". In our model, we use "White" as the baseline for $\mbox{victim\_race}_i$ to see if being part of a minority impacts if the case goes unsolved or not. $\beta_1$ is the coefficient that represents the log-odds when $\mbox{victim\_race}_i$ changes. $\mbox{victim\_age}_i$ is the victim's age, which is a whole number. $\beta_2$ is the log-odds when $\mbox{victim\_age}_i$ increases by 1 year. $\mbox{victim\_sex}_i$ represents the sex of the victim, where in the dataset it is either "female" or "male" and $\beta_3$ is the log-odds when $\mbox{victim\_sex}_i$ changes. $\mbox{city}_i$ is the city the victim was reported to be killed in, which from our dataset could be either "New York" or "Los Angeles". $\beta_4$ is the coefficient that stands for the log-odds when $\mbox{city}_i$ changes. We define $\mbox{year}_i$ to be the year the homicide was reported to have occured from 2010 to 2017. $\beta_5$ indicates the log-odds when $\mbox{year}_i$ increases by 1 year.

Our model runs in R [@citeR] using the rstanarm package [@citerstanarm]. For our model's priors, we use the default priors provided by rstanarm [@citerstanarm]. Diagnostics for the model such as in posterior predictive check, posterior versus prior comparison, trace and Rhat plots can be found in @sec-model-details.

@@

# NOTE: Needed to save diagram and read it in as an image since grViz doesn't render in PDFs
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("../other/sketches/casual_model.png")
plot.new()
rasterImage(the_image, 0,0,1.05,1)
```

However, our model has limitations and there are situations where this model would not work. @fig-causal-model shows that there is a confounder, "resources of investigating team" between the predictor variables, city and year and the outcome variable, case being unsolved. We define "resources of the investigating team" to include any of the following: the amount of people on the team investigating the case, time available allotted to investigate the case, amount of open cases for the team, cost, skill and education levels of members, etc. We currently do not have any information available about the resources of the investigating team for the case and further investigation is needed. We proposed an idealized survey we would conduct to collect the necessary data to further understand the relationship between homicide case characteristics and unsolved homicides in @sec-ideal-survey. If we have information available about the resources of the investigating team for the case, the current model would not work and would need to be revised. This is due to the interaction between the city, year, and outcome variables with the confounder.

@@

\newpage
## Idealized Survey and Methodology {#sec-ideal-survey}
- Link to literature

@@

\newpage 
## Overview and Evaluation of The Washington Post’s Dataset {#sec-data-evalulation}
- TODO: Make sure to link evaluation to literature
